Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-01-06 nips2015.tex
ENH: formula for dual gap

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}

@@

\begin{abstract}
We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum sequential games like Texas Hold'em Poker. %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn Poker.
We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with general convex sets.
\end{abstract}

@@

\paragraph{Plan}
We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.  This is followed by a demonstration on Kuhn Poker in section \ref{sec:kuhn}. In section \ref{sec:algo_gen}, we extend  the algorithm to problems with more general strategy profiles, and exhibit thesame convergence properties.

%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.

%%%
\paragraph{Extensive-form representation}
The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically.
The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
At each node $t$ of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

$a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
We will assume implicitly that each (non-chance) player is rational.

A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts. The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.

\paragraph{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, $\sigma_h$ is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. $C_h$ is the set of choices at $h$. \textit{Perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies. In sequence-form, the strategy profile $Q_k$ of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors satisying
% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
\begin{equation}
    z(\emptyset) = 1 \text{ and }
    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
  \label{eq:lin}
\end{equation}

These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
where $E_k$ is a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$. Thus we can re-write

\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
  \label{eq:poly}
\end{equation}

Each point $z \in Q_k$ is called a \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.

The \textit{payoff matrix} from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
\begin{equation}
    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
  \end{equation}

If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.

The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form. However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.

\paragraph{Example: Sequence-form representation of Kuhn Poker}
\label{sec:kuhn_sf}
The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
$A = \left[\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right]$,\\
$E_1 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
and $E_2 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right]$.\\

\paragraph{Statement of the problem: Nash equilibrium problem in sequence-form}
In sequence-form representation, the Nash equilibrium problem is (see \cite{von1996efficient})
\begin{equation}
  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
  \label{eq:opt_pb}
\end{equation}
As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
\begin{equation}
  x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
\end{equation}
Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
\footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

Even though problem \eqref{eq:opt_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).

@@

%% \section{Statement of the problem}
%% The Nash equilibrium problem for a two-person zero-sum sequential game with imcomplete information and perfect recall is a the saddle-point problem
%% \begin{equation}
%%   \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
%%   \label{eq:opt_pb}
%% \end{equation}

%% where player $k$'s \textit{strategy profile} $Q_k$ is the polytope
%% \begin{equation}
%%   Q_k := \{z \in \mathbb{R}^{n_k}| E_kz = e_k\text{ and } z_j \ge 0 \text{ }\forall j\}
%% \end{equation}
%% for %% some convex subset $C_k$ of a euclidean space $\mathbb{R}^{n_k}$, and 
%% some $p_k$-by-$n_k$ matrix $E_k$ and $p_k$-dimensional vector $e_k$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
%% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projection operators $\Pi_{C_k}$ can be cheaply computed.
%% Typically, $C_k = \mathbb{R}^{p_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint. %% in this case, $\Pi_{C_k}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
%% As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
%% \begin{equation}
%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
%% \end{equation}
%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
%% \paragraph{Simultaneous two-person zero-sum games}
%% \label{subsec:example_games}
%% Here, the Nash equilibrium problem takes the form \eqref{eq:opt_pb} with $p_k = 1$, $C_k = \mathbb{R}^{p_k}_+$, $E_k = 1_{1, n_k}$,
%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).

%% \paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:opt_pb}.

@@

\begin{remark}
  The matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of choices of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of choices of each player will
%% zig-zag between only a limited number of the player's information sets so that a choice at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

%% In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
%% We elaborate our proposed algorithm in section \ref{sec:algo}.

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{qtree}

@@

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration, for computing Nash $\epsilon$-equilibria for two-person zero-sum sequential games like Texas Hold'em Poker, in $\mathcal{O}(1/\epsilon)$ iterations. %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn Poker.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

@@

\paragraph{Nash equilibrium problem in sequence-form}
In \cite{von1996efficient, vonequilibrium}, it was established that for sequential two-person zero-sum games with imcomplete information and perfect recall, there exists sparse matrices $A \in \mathbb{R}^{n_1 \times n_2}, E_1 \in \mathbb{R}^{l_1 \times n_1}, E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are all linear in the size of the game tree (number of states in the game) and such that Nash equilibria correspond to points $(x, y)$ which solve the primal LCP (Linear Constrained Programming) problem
\begin{equation}
  \begin{aligned}
    & \underset{y,p}{\text{minimize}}
    & & e_1^Tp \\
    & \text{subject to}
    & & -Ay + E_1^Tp \geq 0,\\
    &&& E_2y = e_2,\\
    &&& y \ge 0
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP problem
\begin{equation}
  \begin{aligned}
    & \underset{x,q}{\text{maximize}}
    & & -e_2^Tq \\
    & \text{subject to}
    & & -A^Tx + E_2^Tq \leq 0,\\
    &&& E_1x = e_1,\\
    &&& x \ge 0
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}

with duality gap given by
\begin{equation}
  \mathcal{G}(p, q) := e_1^Tp - (-e_2^Tq) = e_1^Tp + e_2^Tq
  \label{eq:dgap}
\end{equation}

$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$. In this representation (called the \textit{sequence-form}), the strategy profile of player $k$ is the polytope
\begin{equation}
  Q_k := \{z \ge 0\text{ }|\text{ }E_kz = e_k\} \subseteq \mathbb{R}^{n_k}
\end{equation}

Of course by \textit{weak duality} in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb},, it holds that
\begin{equation}
  \mathcal{G}(p, q) \geq 0
\end{equation}
for any fixed pair $(x, y)$ of realization plans and admissible dual pair $(p,q)$ in problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb}.

It was also shown (for example, Theorem 3.14 of \cite{vonequilibrium}) that a $(x, y)$ is a solution to the primal-dual problem \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff there exists vectors $p$ and $q$ such that
\begin{equation}
  \begin{split}
    E_1x = e_1,\text{ }x \geq 0,\hspace{1em} E_2y = e_2,\text{ }y \geq 0\\
    -Ay + E_1^Tp \geq 0,\hspace{1em}-A^Tx + E_2^Tq \leq 0
    \end{split}
\end{equation}

Moreover, in this case \textit{strong duality} holds and the value of the game equals $e_1^Tp = -e_2^Tq$,
In this case, the duality gap defined in \eqref{eq:dgap} vanishes.

%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
%% \begin{equation}
%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
%% \label{eq:nash_ineq}
%% \end{equation}
%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

\begin{remark}  
  Even though problem \eqref{eq:primal_pb} is in theory, amendable to classical tools like LCP (\textit{Linear Constraint Programming}), at least for sequential games with imcomplete information the game (e.g Texas Hold'em Poker) is exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
\end{remark}

% For the purpose of completeness we will cover the sequence-form representation in \ref{sec:rep}.

@@

%% \section{Statement of the problem}
%% The Nash equilibrium problem for a two-person zero-sum sequential game with imcomplete information and perfect recall is a the saddle-point problem
%% \begin{equation}
%%   \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
%%   \label{eq:primal_pb}
%% \end{equation}

%% where player $k$'s \textit{strategy profile} $Q_k$ is the polytope
%% \begin{equation}
%%   Q_k := \{z \in \mathbb{R}^{n_k}| E_kz = e_k\text{ and } z_j \ge 0 \text{ }\forall j\}
%% \end{equation}
%% for %% some convex subset $C_k$ of a euclidean space $\mathbb{R}^{n_k}$, and 
%% some $l_k$-by-$n_k$ matrix $E_k$ and $l_k$-dimensional vector $e_k$. $A$ is the \textit{payoff matrix} from player 1's perspective of the game: if player 1 players strategy
%% $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.
%% %% We will assume that the convex sets $C_k$ are simple enough so that the eucliean projection operators $\Pi_{C_k}$ can be cheaply computed.
%% Typically, $C_k = \mathbb{R}^{l_k}_+ := \{x \in \mathbb{R}^n|x_k \ge 0\}$, the \textit{the nonnegative orthant}, and encodes a nonnegativity constraint. %% in this case, $\Pi_{C_k}(z) \equiv (z)_+$ as seen in subsection \ref{sec:notation}.
%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
%% \begin{equation}
%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
%% \end{equation}
%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

%% We can distinguish two categories of such games, in terms of (non-)simultaneity of play.
%% \paragraph{Simultaneous two-person zero-sum games}
%% \label{subsec:example_games}
%% Here, the Nash equilibrium problem takes the form \eqref{eq:primal_pb} with $l_k = 1$, $C_k = \mathbb{R}^{l_k}_+$, $E_k = 1_{1, n_k}$,
%%   and $e_k = 1$, so that $Q_k$ is simply the probabability $n_k$-simplex $\Delta_{n_k}$. Each point in $\Delta_{n_k}$ corresponds to a \textit{mixed-strategy} for player $j$,
%% and represents a randomization on their \textit{pure-strategies} (corresponding to the vertices of their propability simplex $\Delta_{n_k}$).

%% \paragraph{Two-person zero-sum sequential games with imcomplete information and perfect recall}
%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.

@@

Solving problem \eqref{eq:primal_pb} exactly is impossible in practice, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists admissible vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} satisfying
\begin{equation}
  0 \le \mathcal{G}(p^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

\paragraph{Outline of article}
The goal of this article is to device a simple algorithm which produces a Nash $\epsilon$-equilibrium after $\mathcal{O}(1/\epsilon)$ iterations%We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. Then in
In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:approx_pb}. In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.  This is followed by a demonstration on Kuhn Poker in section \ref{sec:kuhn}. In section \ref{sec:algo_gen}, we extend  the algorithm to problems with more general strategy profiles, and exhibit thesame convergence properties.

%% It is now known, thanks to the \textit{sequence-form representaion}, that the Nash equilibrium problem for such games takes the form \eqref{eq:primal_pb}.

%%%
%% \section{The sequence-form representation}
%% \label{sec:rep}
%% \paragraph{Recap: Extensive-form representation} The game tree $\mathcal{T}$ is defined as follows. There are three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically. Nodes of the game tree $\mathcal{T}$ are identified with states of the game, and actions taken by players correspond to edges of $\mathcal{T}$.
%% The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
%% At each node $t$ of $\mathcal{T}$, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

%% $a(t)$ is the \textit{payoff} received by player $1$ at node $t$. That the game is zero-sum means that player 2
%% receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes, since the game must continue.
%% The goal of a \textit{rational} player is that the game should end at a node for which her payoff is as large as possible.
%% We will assume implicitly that each (non-chance) player is rational.

%% A \textit{mixed-strategy} for a player is specified by a prescription of the probability of making a given choice from a given node at which the player acts. The chance player plays a publicly known \textit{mixed strategy} $\beta_0$.

%% \paragraph{From extensive-form to sequence-form representation}
%% For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
%% \begin{equation}
%% \mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
%% \end{equation}
%% Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
%% $\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

%% Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies. In sequence-form, the strategy profile $Q_k$ of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors satisying
%% % Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
%% \begin{equation}
%%     z(\emptyset) = 1 \text{ and }
%%     z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
%%   \label{eq:lin}
%% \end{equation}

%% These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
%% where $E_k$ is a matrix with $l_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $l_k$-dimensional vector of the form $(1, 0, ..., 0)$. Thus we can re-write

%% \begin{equation}
%%   Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
%%   \label{eq:poly}
%% \end{equation}

%% Each point $z \in Q_k$ is called a \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
%% \begin{equation}
%%   \beta_k(h, c) := \begin{cases}
%%     z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
%%     0, &\mbox{Otherwise}.
%%   \end{cases}
%% \end{equation}

%% From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.

%% The payoff matrix from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
%% \begin{equation}
%%     A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
%%   \end{equation}

%% If player 1 plays strategy $x \in Q_1$ and player 2 plays strategy $y \in Q_2$ then player 1 gets $x^TAy$ units of money; that the game is ``zero-sum'' means that player 2 gets $-x^TAy$.

%% The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form. However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.
